### 2019-06-24 README.Rmd
Started step 2 of README

First we will use the *get_kegg* function access the KEGG REST API and download the data sets required to perform 
our downstream analysis. This function takes two arguments. The first, 'species' is required and is the species of 
interest. Currently, *diffEnrich* supports three species, and the argument is a character string using the KEGG
code [REF](https://www.pnas.org/content/suppl/2008/09/11/0806162105.DCSupplemental/ST1_PDF.pdf): 
Homo sapiens (human), use 'hsa'; Mus musculus (mouse), use 'mmu', and Rattus norvegicus (rat), use 'rno'. The second,
'path' is also passed as a character string, and is the path of the directory in which the user would like to
write the data sets downloaded from the KEGG REST API. If the user does not provide a path, the data sets will 
be automatically written to the current working directory using the *here::here()* functionality. These data 
sets will be tab delimited files with a name describing the data, and for reproducibility, the date they were generated
and the version of KEGG when the API was accessed. In addition to these flat files, *get_kegg* will also
create a named list with the three relavent KEGG data sets. The names of this list will describe the the data set.

@@

>>>>

### Step 1: Collect and clean pathways from KEGG API
First we will use the *get_kegg* function access the KEGG REST API and download the data sets required to perform 
our downstream analysis. This function takes two arguments. The first, 'species' is required and is the species of 
interest. Currently, *diffEnrich* supports three species, and the argument is a character string using the KEGG
code [REF](https://www.pnas.org/content/suppl/2008/09/11/0806162105.DCSupplemental/ST1_PDF.pdf): 
Homo sapiens (human), use 'hsa'; Mus musculus (mouse), use 'mmu', and Rattus norvegicus (rat), use 'rno'. The second,
'path' is also passed as a character string, and is the path of the directory in which the user would like to
write the data sets downloaded from the KEGG REST API. If the user does not provide a path, the data sets will 
be automatically written to the current working directory using the *here::here()* functionality. These data 
sets will be tab delimited files with a name describing the data, and for reproducibility, the date they were generated
and the version of KEGG when the API was accessed. In addition to these flat files, *get_kegg* will also
create a named list with the three relavent KEGG data sets. The names of this list will describe the the data set.

@@

### Step 2: Perform individual enrichment analysis

In this step we will use the *pathEnrich* function to identify KEGG pathways that are enriched based on a list of genes we
are interested in and based on a list of background genes. This function may not always use the complete list of genes provided 
by the user. Specifically, it will only use the genes from the list provided that are also in
the most current species list pulled from the KEGG REST API using *get_kegg*, or from the older KEGG data loaded by the user from a 
previous *get_kegg* call. The *pathEnrich* function should be run at least twice, once for the genes of interest and once for the background.
Each *pathEnrich* call generates a dataframe summarizing the results of a traditional pathway enrichment analysis in which a Fisher's
Exact test is used to identify which KEGG pathways are enriched by the user's list of interesting genes with repect to background
enrichment.

```{r pathEnrich}
# run pathEnrich using kegg_rno
## Genes of interest
sig_pe <- pathEnrich(gk_obj = kegg, gene_list = geneLists$sigGenes)
## Background
bkg_pe <- pathEnrich(gk_obj = kegg, gene_list = geneLists$background)
head(sig_pe)
```

*pathEnrich* generates a dataframe with 9 columns described below.
